1. Write a R code to Generate 6X6 matrix (A) using the random numbers between 1 to 100 & generate another 6x6 matrix (B) using random numbers between 500 to 600.
(20 Marks)
  a. Find the range of matrices A and B.
  b. Find the max value from each row of the matrices A and B.
  c. Find the diagonal values of matrices A&B.
  d. Multiply matrices A and B
  e. Replace the 4th row of Matrix A with diagonal values of matrix B
  f. Multiply matrices A & B and store the values on X.
  g. Divide the matrix A with matrix B.

```{r}
n<-c(1:100)
h<-c(500:600)
A_matric <- matrix(n, 6, 6)
A_matric
B_matric <- matrix(h, 6, 6)
B_matric

# a.Find the range of matrices A and B.
range(A_matric)
range(B_matric)

# b.Find the max value from each row of the matrices A and B.
apply(A_matric,1,max)
apply(B_matric,1,max)

# c. Find the diagonal values of matrices A&B.
diag(A_matric)
diag(B_matric)

# d. Multiply matrices A and B
A_matric %*% B_matric
multip
# e. Replace the 4th row of Matrix A with diagonal values of matrix B
A_matric[4, ] <- diag(t(B_matric))
A_matric

# f. Multiply matrices A & B and store the values on X.
X <- A_matric %*% B_matric
X
# g. Divide the matrix A with matrix B.
A_matric/B_matric
```

2. Create a table using dataframe/tibble with the following categories(a to f) (10 marks)
  First name, 
  Second Name, 
  Age,
  Occupation, 
  Place,
  Random numbers( between 1 to 10)
And input at least 10 samples(observation) and do the following
  Extract the last column (f)
  Find the sum, mean and length of the extracted column


```{r}
fname<-c("sang", "hann", "seng", "pic", "ask", "know", "help", "hello", "hi", "llala")
sname<-c("sonyratt", "manich", "rathanak", "me", "you", "haha", "jeje", "nyra", "nara", "lelelola")
age<-c(12,13,10,30,20,30,5,49,12,39)
occupation<-c("docter", "software engineer", "seller", "manager", "teacher", "deliver", "chef", "ower", "dentist", "preparator")
place<-c("siem reap", "kompot", "takeo", "battombong", "preveng", "bonteay meanjey", "preas vihar", "phnom penh", "kompong speu", "katmav")
num<-(1:10)
data<-data.frame(a=fname, b=sname, c=age, d=occupation, e=place, f=num)

# Extract the last column (f)
last_colum<-data$f
last_colum

#Find the sum, mean and length of the extracted column
#sum
sum=0
for(i in last_colum) {
  sum = sum + i
}
sum

#mean
mean<-mean(last_colum)
mean

#length
length<-length(last_colum)
length

```



3. Create a .txt file (Minimum : 150 words) with the latest news (In English) in cambodia from the official news agency’s website(Note: Include the reference link) and do the following (20 Marks)
  a. Read the .txt file
  b. Perform the Tokenization & count the words
  c. Identify the most repeated word and replace that word with “KIT”
  d. Perform the Sentiment analysis
  e. Plot the graph between “words count” and “words” using geom_col()
    e.1. X-axis title =“Number of words”, Size=10, Bold, Text in Blue color, Center, space between graph and title = 20.
	  e.2. Y-axis title =“List of words”, Size=10, Bold, Text in Red color, Center, space between graph and title = 20.
	  e.3. Graph title =”Text Mining using R”,Size = 25, Bold, Center, Text in Yellow color, space between graph and title = 25.


```{r}
library(tokenizers)
# a. Read the .txt file
# text from url: https://www.phnompenhpost.com/national/mekong-levels-set-drop-during-power-grid-work
data <- read.delim("C:/Users/sang sonyratt/Downloads/3.txt")
data

#b. Perform the Tokenization count the words
words <- paste0(data)
words_tokens <- tokenize_words(words)
count <- count_words(words)
count

#c. Identify the most repeated word and replace that word with “KIT”
#Identify the most repeated word
most_repeated_words <- names(table(words_tokens))[as.vector(table(words_tokens))==max(table(words_tokens))]
most_repeated_words_count <- max(table(words_tokens))
most_repeated_words
most_repeated_words_count

#replace that word with “KIT”
subs <- gsub(most_repeated_words, "KIT", words_tokens)
subs

#d. Perform the Sentiment analysis
library(sentimentr)
sentiment_analysis <- sentiment(words)
sentiment_analysis

#e. Plot the graph between “words count” and “words” using geom_col()
  #e.1. X-axis title =“Number of words”, Size=10, Bold, Text in Blue color, Center, space between graph and title = 20.
  #e.2. Y-axis title =“List of words”, Size=10, Bold, Text in Red color, Center, space between graph and title = 20.
  #e.3. Graph title =”Text Mining using R”,Size = 25, Bold, Center, Text in Yellow color, space between graph and title = 25.

ggplot(aes(words_tokens, count)) +
         geom_col() +
         them(
           axis.title.x=element_text(size=20, color="blue", face="bold", hjust=0.5, margin=margin(t=20),
           axis.title.y=element_text(size=20, color="red", face="bold", hjust=0.5, margin=margin(r=20),
          plot.title=element_text(size=25, color="yellow", face="bold", hjust=0.5, margin=margin(b=20)))
         ))

```

4. Find the assigned Dataset from the list below and perform the following (20 Marks)
  a. Import and Clean the dataset.
  b. Find the x and y variables(axis) from the assigned dataset and give the reason for selecting the x and y axis. 
  c. Plot the graph using geom_col() and perform the linear model in statistics.
  d. Perform the facet with the available columns(Choose the any two variables from the columns)
  e. Use the theme layer to do the following (Note: Based on dataset, name the x and y axis & graph)
    e.1. x-axis title =“________”, Size=10, Bold, Text in Green color, Center, space between graph and title = 20.
	  e.2. y-axis title =“________”, Size=10, Bold, Text in Yellow color, Center, space between graph and title = 20.
	  e.3. Graph title =”_________”,Size = 25, Bold, Center, Text in Blue color, space between graph and title = 25.

### Answer: 
b. I choose to state as x and forecast_prob for y from the assigned dataset because we plot this two varaibles we can see the data of forecast probability of each State from the given dataset

```{r}
dataset <- read_csv("C:/Users/sang sonyratt/Downloads/data/forecast-methodology/historical-senate-predictions.csv")
dataset
is.na(dataset)

ggplot(dataset, aes(state, forecast_prob)) +
  geom_col() +
  geom_smooth(method="lm") +
  facet_grid(result ~ year) +
  xlab("State") + 
  ylab("Forecast probability") +
  ggtitle("historical-senate-predictions") +
  theme(
    axis.title.x = element_text(color = "green", size = 10, face = "bold", hjust = 0.5, margin = margin(t=20)),
    axis.title.y = element_text(color = "yellow", size = 10, face = "bold", hjust = 0.5, margin = margin(r=20)),
    plot.title = element_text(color = "blue", size = 25, face = "bold", hjust = 0.5, margin = margin(b=25))
  ) + ggsave(filename="sangsonyratt.png", units="cm", width=25, height=25)
```
